Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
cleaning up cleanup of section 3

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.

@@

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.  We follow the second approach.
In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  To overcome these bounds, we use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon_{ext}$.
\end{definition}

@@

\begin{lemma}
\label{lem:cond and cext}
Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.  Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.  Define $(\gen, \rep)$ as:
\begin{itemize}
\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
\end{itemize}
Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
\end{lemma}

>>>>

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse\le 0$ is an open problem.

@@

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.  We follow the second approach.
In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  To overcome these bounds, we use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\begin{lemma}
\label{lem:cond and cext}
Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.  Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.  Define $(\gen, \rep)$ as:
\begin{itemize}
\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
\end{itemize}
Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
\end{lemma}
